\documentclass[10pt,a4paper]{article}

\usepackage[margin=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{tabularx}

\definecolor{accent}{HTML}{1A5276}
\hypersetup{colorlinks=true,urlcolor=accent,linkcolor=accent}
\titleformat{\section}{\large\bfseries\color{accent}}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{8pt}{4pt}
\setlist[itemize]{nosep,left=0pt,label=\textbullet,topsep=2pt}
\pagestyle{empty}
\setlength{\parindent}{0pt}

\begin{document}

\begin{center}
  {\LARGE\bfseries Foad S. Farimani, PhD} \\[3pt]
  {\small Systems Engineer \& Architect\enspace$\cdot$\enspace Hardware Inventor\enspace$\cdot$\enspace Robotics \& Precision Manufacturing}
  \\[3pt]
  {\footnotesize
    Apeldoorn, Netherlands\enspace$\mid$\enspace
    Dutch citizen\enspace$\mid$\enspace
    +31\,614685010\enspace$\mid$\enspace
    \href{mailto:f.s.farimani@gmail.com}{f.s.farimani@gmail.com}\enspace$\mid$\enspace
    \href{https://linkedin.com/in/fsfarimani}{LinkedIn}\enspace$\mid$\enspace
    \href{https://github.com/Foadsf}{GitHub}
  }
\end{center}

\section{Profile}
I'm a systems engineer and a lifelong inventor. I filed my first two robotics patents in Iran in my twenties, then designed a robot motor that runs on nothing but air, no metal, no electronics, fast enough to drive a surgical robot inside a live MRI scanner. I bring that blank-page-to-shipped instinct to the world's most demanding precision manufacturing, ASML's lithography machines, where I solve the hard physical problems, build the engineering capabilities, and open the funding that lets a company punch above its weight. I move fluently across the whole stack: systems architecture, CAD/CAE/CAM/PLM, mechanism and actuation design, manufacturing, and the teams that make it real.

\section{Signature Achievements}
\begin{itemize}
  \item \textbf{Invented PneuAct}, a new class of MRI-compatible pneumatic stepper motor. No metal, no electronics, no lubrication, fully 3D-printed, 850 RPM. IEEE ICRA 2018 and RA-L 2020; featured on Hackaday and U-Today.
  \item \textbf{Doubled the fatigue life} of a critical ASML flexure by root-causing a failure everyone else had only patched (EDM recast layer) and fixing it at the metallurgy. ASML credited the result at its 2024 Technology Conference.
  \item \textbf{Built the Research Funding Initiative} at NTS from a blank page, a pipeline connecting the company's engineering to EU and national R\&D money that put ~40 funding opportunities on the table.
\end{itemize}

\section{Experience}

\textbf{System Lead Engineer} \hfill NTS D\&E, Hengelo \\
{\small\textit{Tier-1 ASML supplier, high-precision manufacturing systems}} \hfill {\small Mar 2022--Present}
\begin{itemize}
  \item Doubled the fatigue life of a critical Inconel 718 flexure by hunting a recurring failure down to its root cause in the metallurgy and killing it at the source; ASML credited the result at its 2024 Technology Conference.
  \item Built NTS's Research Funding Initiative from nothing: a pipeline linking the company's engineering strengths to EU and Dutch R\&D money (Chips JU, Horizon Europe, ChipTech Twente), with ~40 opportunities screened, and spun out the Surface Treatment Lab business case.
  \item Chair the Surface Treatment competence, standing up NTS's in-house precision-finishing capability (electropolishing, plasma polishing, passivation, precision cleaning) and the supplier network behind it.
  \item Co-founded the FEM/CAE competence team and seeded the Fluidics and Mechanical Engineering clusters, then introduced MBSE across the group.
  \item Ran systems engineering and architecture for the EXE:5200 sensor assembly, from design kickoff and 12NC structure through release.
\end{itemize}

\vspace{4pt}
\textbf{Lead Mechanical Engineer} \hfill VDL ETG T\&D \\
{\small\textit{Precision mechanics, tooling, and ASML equipment development}} \hfill {\small Jul 2020--Feb 2022}
\begin{itemize}
  \item Led a multi-engineer team that cracked the densest cable-and-hose routing problem in ASML's EXE5000, building the integration tooling end to end, from fixtures and molds to supplier and manufacturability sign-off.
  \item Designed the precision leaf-spring mechanics behind YieldStar 500's optical fiducials, where microns of stiffness decide whether the metrology hits alignment.
  \item Shaped the early VES force-decoupler bellows, the parts that keep a precision stage from shaking itself apart, balancing pressure, stiffness, and what suppliers could actually build.
\end{itemize}

\vspace{4pt}
\textbf{PhD Researcher, Surgical Robotics} \hfill University of Twente \\
{\small\textit{MRI-compatible surgical robotics and pneumatic actuation}} \hfill {\small 2016--2020}
\begin{itemize}
  \item Invented PneuAct: a 3D-printed pneumatic stepper motor with no metal and no electronics, running at 850 RPM safely inside an MRI scanner. Published at IEEE ICRA and RA-L; featured on Hackaday and U-Today.
  \item Designed and prototyped patient-mounted surgical robots end to end: mechanism, actuation, sensing, and control.
  \item Delivered research inside the EU's EUR 4.34M MURAB consortium (robotic MRI and ultrasound biopsy), plus the PneuARMM and PanoSurg grants.
\end{itemize}

\section{Patents}
Filed early in my career in Iran, years before the PhD:
\begin{itemize}
  \item "MRI Compatible Surgery Assistant Robot", IR 100300442.
  \item "Drugs Injection Smart Robot", IR 100300872.
\end{itemize}

\section{Selected Publications}
\begin{itemize}
  \item "PneuAct-II: Hybrid Manufactured Electromagnetically Stealth Pneumatic Stepper Actuator", IEEE Robotics and Automation Letters, 2020. doi:10.1109/LRA.2020.2974714
  \item "Introducing PneuAct: Parametrically-Designed MRI-Compatible Pneumatic Stepper Actuator", IEEE ICRA, 2018. doi:10.1109/ICRA.2018.8461116
  \item "Frictional characteristics of Fusion Deposition Modeling (FDM) manufactured surfaces", Rapid Prototyping Journal, 2020. doi:10.1108/RPJ-06-2019-0171
  \item "Magnetic Resonance Compatible Pneumatic Actuators for Surgical Robotics", PhD thesis, University of Twente.
\end{itemize}

\section{Technical Skills}
{\small
\begin{tabularx}{\textwidth}{@{}lX@{}}
  \textbf{Systems engineering:} & Architecture, requirements, interfaces, MBSE, design reviews (PDR/CDR), V\&V, configuration and release \\
  \textbf{Design \& PLM:} & CAD (Siemens NX, SolidWorks, CATIA), CAE/FEM (ANSYS/APDL), CAM, PLM/PDM \\
  \textbf{Robotics \& hardware:} & Novel actuator and mechanism design, pneumatic actuation, compliant mechanisms, sensing, motion control, rapid prototyping, 3D printing \\
  \textbf{Manufacturing:} & Design-for-manufacture, precision tooling, fixtures and molds, surface treatment, supplier and manufacturability closure \\
  \textbf{Leadership:} & Team and competence leadership, R\&D funding strategy, stakeholder alignment \\
\end{tabularx}
}

\section{Education}
\textbf{PhD, Surgical Robotics}, University of Twente, Enschede \hfill 2016--2020 \\[2pt]
\textbf{MSc, Biomedical Engineering}, Amirkabir University of Technology, Tehran \hfill 2006--2009 \\[2pt]
\textbf{BSc, Mechanical Engineering}, Sharif University of Technology, Tehran \hfill 2000--2006

\end{document}
