\documentclass[10pt,a4paper]{article}

\usepackage[margin=0.55in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{tabularx}

\definecolor{accent}{HTML}{1A5276}
\hypersetup{colorlinks=true,urlcolor=accent,linkcolor=accent}
\titleformat{\section}{\large\bfseries\color{accent}}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{6pt}{4pt}
\setlist[itemize]{nosep,left=0pt,label=\textbullet,topsep=2pt}
\pagestyle{empty}
\setlength{\parindent}{0pt}

\begin{document}

\begin{center}
  {\LARGE\bfseries Foad S. Farimani, PhD} \\[3pt]
  {\small Systems Engineer \& Architect\enspace$\cdot$\enspace Hardware Inventor\enspace$\cdot$\enspace Robotics \& Precision Manufacturing}
  \\[3pt]
  {\footnotesize
    Apeldoorn, Netherlands\enspace$\mid$\enspace
    Dutch citizen\enspace$\mid$\enspace
    +31\,614685010\enspace$\mid$\enspace
    \href{mailto:f.s.farimani@gmail.com}{f.s.farimani@gmail.com}\enspace$\mid$\enspace
    \href{https://linkedin.com/in/fsfarimani}{LinkedIn}\enspace$\mid$\enspace
    \href{https://github.com/Foadsf}{GitHub}\enspace$\mid$\enspace
    \href{https://stackoverflow.com/users/4999991}{Stack Overflow}
  }
\end{center}

\section{Summary}
I'm a systems engineer and a lifelong inventor. I filed my first two robotics patents in Iran in my twenties, then designed a robot motor that runs on nothing but air, no metal, no electronics, fast enough to drive a surgical robot inside a live MRI scanner (IEEE ICRA, RA-L, picked up by Hackaday). I bring that blank-page-to-shipped instinct to the world's most demanding precision manufacturing: for ASML's machines I doubled the fatigue life of a critical flexure (credited at ASML's 2024 Technology Conference), chair the surface-treatment competence, and built a research-funding pipeline that opened EU and national R\&D programs for the company. I move fluently across CAD, CAE, CAM, and PLM, and I lead the teams that turn ideas into hardware.

\section{Experience}

\textbf{System Lead Engineer} \hfill NTS D\&E, Hengelo \\
{\small\textit{Tier-1 ASML supplier, high-precision manufacturing systems}} \hfill {\small Mar 2022--Present}
\begin{itemize}
  \item Doubled the fatigue life of a critical Inconel 718 flexure by hunting a recurring failure down to its root cause in the metallurgy and killing it at the source; ASML credited the result at its 2024 Technology Conference.
  \item Built NTS's Research Funding Initiative from nothing: a pipeline linking the company's engineering strengths to EU and Dutch R\&D money (Chips JU, Horizon Europe, ChipTech Twente), with ~40 opportunities screened.
  \item Chair the Surface Treatment competence, standing up NTS's in-house precision-finishing capability and the supplier network behind it.
  \item Run systems engineering and architecture on ASML module programs, from requirements and design reviews through release.
\end{itemize}

\vspace{4pt}
\textbf{Lead Mechanical Engineer} \hfill VDL ETG T\&D \\
{\small\textit{Precision mechanics, tooling, and ASML equipment development}} \hfill {\small Jul 2020--Feb 2022}
\begin{itemize}
  \item Led a multi-engineer team that cracked the densest cable-and-hose routing problem in ASML's EXE5000, building the integration tooling end to end, from fixtures and molds to supplier and manufacturability sign-off.
  \item Designed the precision leaf-spring mechanics behind YieldStar 500's optical fiducials, where microns of stiffness decide whether the metrology hits alignment.
  \item Shaped the early VES force-decoupler bellows, the parts that keep a precision stage from shaking itself apart, balancing pressure, stiffness, and what suppliers could actually build.
\end{itemize}

\vspace{4pt}
\textbf{PhD Researcher, Surgical Robotics} \hfill University of Twente \\
{\small\textit{MRI-compatible surgical robotics and pneumatic actuation}} \hfill {\small 2016--2020}
\begin{itemize}
  \item Invented PneuAct: a 3D-printed pneumatic stepper motor with no metal and no electronics, running at 850 RPM safely inside an MRI scanner. Published at IEEE ICRA and RA-L; featured on Hackaday and U-Today.
  \item Designed and prototyped patient-mounted surgical robots end to end: mechanism, actuation, sensing, and control.
  \item Delivered research inside the EU's EUR 4.34M MURAB consortium (robotic MRI and ultrasound biopsy), plus the PneuARMM and PanoSurg grants.
\end{itemize}

\section{Education}

\textbf{PhD, Surgical Robotics}, University of Twente, Enschede \hfill 2016--2020 \\[2pt]
\textbf{MSc, Biomedical Engineering}, Amirkabir University of Technology, Tehran \hfill 2006--2009 \\[2pt]
\textbf{BSc, Mechanical Engineering}, Sharif University of Technology, Tehran \hfill 2000--2006

\section{Technical Skills}
{\small
\begin{tabularx}{\textwidth}{@{}lX@{}}
  \textbf{Systems engineering:} & Architecture, requirements, interfaces, MBSE, design reviews (PDR/CDR), V\&V, configuration and release \\
  \textbf{Design \& PLM:} & CAD (Siemens NX, SolidWorks, CATIA), CAE/FEM (ANSYS/APDL), CAM, PLM/PDM \\
  \textbf{Robotics \& hardware:} & Novel actuator and mechanism design, pneumatic actuation, compliant mechanisms, sensing, motion control, rapid prototyping, 3D printing \\
  \textbf{Manufacturing:} & Design-for-manufacture, precision tooling, fixtures and molds, surface treatment, supplier and manufacturability closure \\
  \textbf{Leadership:} & Team and competence leadership, R\&D funding strategy, stakeholder alignment \\
\end{tabularx}
}

\end{document}
