\documentclass[11pt,a4paper]{article}

\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{tabularx}
\usepackage{fancyhdr}

\definecolor{accent}{HTML}{1A5276}
\hypersetup{colorlinks=true,urlcolor=accent,linkcolor=accent}
\titleformat{\section}{\Large\bfseries\color{accent}}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{10pt}{6pt}
\titleformat{\subsection}{\large\bfseries}{}{0em}{}
\titlespacing*{\subsection}{0pt}{6pt}{3pt}
\setlist[itemize]{nosep,left=0pt,label=\textbullet,topsep=2pt}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{\footnotesize Foad S. Farimani, Mechatronics Systems CV, Page \thepage}
\setlength{\parindent}{0pt}

\begin{document}

\begin{center}
 {\LARGE\bfseries Foad S. Farimani, PhD} \\[4pt]
 {\small Mechatronics System Engineer\enspace$\mid$\enspace Test \& Validation Tooling\enspace$\mid$\enspace Hardware/Software Interfaces}
 \\[6pt]
 {\small
  Apeldoorn, Netherlands\enspace$\mid$\enspace
  Dutch citizen\enspace$\mid$\enspace
  +31\,614685010\enspace$\mid$\enspace
  \href{mailto:f.s.farimani@gmail.com}{f.s.farimani@gmail.com}\enspace$\mid$\enspace
  \href{https://linkedin.com/in/fsfarimani}{linkedin.com/in/fsfarimani}\enspace$\mid$\enspace
  \href{https://github.com/Foadsf}{github.com/Foadsf}
 }
\end{center}

\section{Professional Profile}
Mechatronics engineer who connects mechanical design, sensors, test hardware, and software behavior into validated production tooling for ASML lithography modules. At NTS, owns qualification tooling workstreams, Safety PLC Emulator validation, and EXE:5200 sensor assembly coordination. PhD background in MRI-compatible pneumatic surgical robotics, actuation, sensing, data acquisition, and experimental validation.

\section{Selected Systems and Mechatronics Work}
\begin{tabularx}{\textwidth}{@{}p{0.26\textwidth}X@{}}
\textbf{Qualification tooling} &
Owned qualification tooling workstreams for ASML modules, connecting pressure decay, particle validation, electrical and mechanical checks, HMI behavior, and acceptance criteria. \\[4pt]
\textbf{Safety PLC Emulator} &
Bridged mockup design, hardware-in-the-loop testing, and software validation needs in the Safety PLC Emulator workstream. \\[4pt]
\textbf{EXE:5200 sensor assembly} &
Performed system engineering for the sensor assembly, including design kickoff, part-numbering, and release-planning coordination. \\[4pt]
\textbf{Surgical robotics} &
Designed MRI-compatible pneumatic actuators and patient-mounted robotic concepts using mechanical design, rapid prototyping, sensing, and experimental validation. \\
\end{tabularx}

\section{Professional Experience}

\subsection{System Lead Engineer, NTS D\&E, Hengelo}
{\small\textit{Tier-1 ASML supplier, high-precision manufacturing systems}} \hfill {\small Mar 2022--Present}
\begin{itemize}
 \item Owned qualification tooling workstreams for ASML modules, connecting pressure decay, particle validation, electrical and mechanical checks, HMI behavior, and acceptance criteria.
 \item Performed system engineering for the EXE:5200 sensor assembly, including design kickoff, part-numbering, and release-planning coordination.
 \item Bridged mockup design, hardware-in-the-loop testing, and software validation needs in the Safety PLC Emulator workstream.
 \item Resolved a fatigue life risk in Inconel 718 E-pin folded leaf springs by tracing failures to EDM recast layer, coordinating plasma polishing and Kolsterising/K33 trials, and validating 2x life improvement on representative leaf springs; recognized at ASML's Technology Conference 2024.
\end{itemize}

\subsection{Lead Mechanical Engineer, VDL ETG T\&D}
{\small\textit{Precision mechanics, tooling, and ASML equipment development}} \hfill {\small Jul 2020--Feb 2022}
\begin{itemize}
 \item Developed precision-mechanics concepts and calculation packages for YieldStar 500 fiducial interfaces, including leaf-spring stiffness, geometry trade-offs, and tolerance-sensitive optical/mechatronic interfaces.
 \item Led EXE5000 cable slab integration tooling workstreams across fixtures, hose and cable preforming, molds, CAD interfaces, supplier feedback, and manufacturability closure.
 \item Interpreted bellows, pressure-drop, stiffness, and force-decoupler behavior for early-stage ATCM/VES mechanical concepts.
\end{itemize}

\subsection{PhD Researcher, University of Twente}
{\small\textit{MRI-compatible surgical robotics and pneumatic actuation}} \hfill {\small 2016--2020}
\begin{itemize}
 \item Designed and tested MRI-compatible pneumatic stepper actuators, patient-mounted robot concepts, sensor interfaces, and experimental setups.
 \item Authored peer-reviewed work on MRI-compatible pneumatic actuation and holds patents on MRI-compatible surgery assistant and drug-injection robot concepts.
 \item Contributed to the EU Horizon 2020 MURAB consortium on MRI and ultrasound robotic assisted biopsy, with a EUR 4.34M project budget.
\end{itemize}

\subsection{Researcher, TU Eindhoven}
{\small\textit{MRI-guided minimally invasive surgical robotics}} \hfill {\small Aug 2012--Feb 2014}
\begin{itemize}
 \item Developed patient-mounted MRI-compatible robotic concepts and supporting sensing/mechanism design.
 \item Worked at the boundary between mechanical design, control-oriented reasoning, and clinical-intervention constraints.
\end{itemize}

\section{Skills}
\begin{tabularx}{\textwidth}{@{}lX@{}}
\textbf{Systems} & Requirements, interfaces, validation rationale, acceptance criteria, system decomposition, MBSE literacy \\
\textbf{Test tooling} & Qualification tooling, pressure decay, particle validation, Golden Sample calibration, HMI behavior, HIL/mockup thinking \\
\textbf{Mechatronics} & Sensors, pneumatic actuation, compliant mechanisms, precision mechanics, control-oriented experiments \\
\textbf{Software} & C\#/.NET/WPF, Python, MATLAB, Git, NXOpen context, data analysis, technical documentation \\
\textbf{CAD/CAE} & Siemens NX, SolidWorks, CATIA, ANSYS/APDL context, rapid prototyping \\
\end{tabularx}

\section{Education}
\textbf{PhD}, University of Twente, Enschede \hfill 2016--2020 \\
{\small Surgical Robotics Laboratory } \\[2pt]
\textbf{MSc, Biomedical Engineering}, Amirkabir University of Technology, Tehran \hfill 2006--2009 \\
\textbf{BSc, Mechanical Engineering}, Sharif University of Technology, Tehran \hfill 2000--2006

\section{Selected Publications and Patents}
\begin{itemize}
 \item PneuAct-II: Hybrid Manufactured Electromagnetically Stealth Pneumatic Stepper Actuator.
 \item Introducing PneuAct: Parametrically-Designed MRI-Compatible Pneumatic Stepper Actuator.
 \item Patent: MRI-Compatible Surgery Assistant Robot.
 \item Patent: Drugs Injection Smart Robot.
\end{itemize}

\end{document}
