\documentclass[11pt,a4paper]{article}

\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{tabularx}
\usepackage{fancyhdr}

\definecolor{accent}{HTML}{2B5797}
\hypersetup{colorlinks=true,urlcolor=accent,linkcolor=accent}
\titleformat{\section}{\Large\bfseries\color{accent}}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{10pt}{6pt}
\titleformat{\subsection}{\large\bfseries}{}{0em}{}
\titlespacing*{\subsection}{0pt}{6pt}{3pt}
\setlist[itemize]{nosep,left=0pt,label=\textbullet,topsep=2pt}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{\footnotesize Foad S. Farimani, Curriculum Vitae, Page \thepage}
\setlength{\parindent}{0pt}

\begin{document}

\begin{center}
 {\LARGE\bfseries Foad S. Farimani, PhD} \\[4pt]
 {\small Technical Program Manager\enspace$\mid$\enspace R\&D Leadership \& Systems Delivery}
 \\[6pt]
 {\small
  Apeldoorn, Netherlands\enspace$\mid$\enspace
  Dutch citizen\enspace$\mid$\enspace
  +31\,614685010\enspace$\mid$\enspace
  \href{mailto:f.s.farimani@gmail.com}{f.s.farimani@gmail.com}\enspace$\mid$\enspace
  \href{https://linkedin.com/in/fsfarimani}{linkedin.com/in/fsfarimani}\enspace$\mid$\enspace
  \href{https://github.com/Foadsf}{github.com/Foadsf}\enspace$\mid$\enspace
  \href{https://stackoverflow.com/users/4999991}{Stack Overflow}
 }
\end{center}

\section{Professional Summary}
Technical program manager who coordinates cross-functional delivery in ASML's tier-one supply chain. At NTS, built an R\&D funding initiative screening 40+ EU/Dutch calls, chaired surface treatment coordination, and drove qualification tooling workstreams from requirements through acceptance criteria and review closure. At VDL ETG, coordinated concurrent engineering for precision opto-mechanical systems. Previously managed EU Horizon 2020 consortium participation and hospital-facing surgical-robotics projects with EUR 4M+ budgets.

\section{Professional Experience}

\subsection{System Lead Engineer, NTS D\&E, Hengelo}
{\small\textit{Tier-1 ASML supplier, high-precision manufacturing systems}} \hfill {\small Mar 2022--Present}
\begin{itemize}
 \item Built Research Funding Initiative concept linking NTS precision-manufacturing competences to EU/Dutch R\&D programs and screened about 40 opportunities.
 \item Owned qualification tooling workstreams connecting requirements, acceptance criteria, pressure decay, particle validation, HMI behavior, and review closure.
 \item Chaired the Surface Treatment team and mapped supplier/process options for electropolishing, plasma polishing, passivation, acid etching, and precision cleaning.
 \item Represented NTS in ASML Technology Angels team, providing strategic business roadmap input and driving internal competence-building activities.
\end{itemize}

\subsection{Lead Mechanical Engineer, VDL ETG T\&D, Hengelo}
{\small\textit{ASML supplier, precision opto-mechanical systems}} \hfill {\small Jul 2020--Feb 2022}
\begin{itemize}
 \item Led EXE5000 cable slab integration tooling workstreams across fixtures, hose/cable preforming, molds, CAD interfaces, supplier feedback, and manufacturability closure.
 \item Developed precision-mechanics concepts and calculation packages for YieldStar 500 fiducial interfaces.
 \item Specialized in sheetmetal design, additive manufacturing, and rapid prototyping.
 \item Implemented advanced fastener techniques including bolt calculation, welding, and glued connections.
 \item Contributed to agile development and concurrent engineering processes.
\end{itemize}

\subsection{PhD Researcher, University of Twente, Enschede}
{\small\textit{Surgical Robotics Laboratory, MRI-compatible Robotic Systems}} \hfill {\small Dec 2015--Mar 2020}
\begin{itemize}
 \item Developed PneuAct system: additively manufactured pneumatic stepper actuator for MRI-guided interventions.
 \item Created PneuARMM platform for pneumatically actuated robotic surgeries.
 \item Received EUR 70K healthcare innovation grant for PneuARMM in collaboration with UT and MST Enschede.
 \item Managed rapid prototyping lab, supervising CNC operations and 3D printing capabilities.
 \item Supervised and mentored multiple MSc and BSc students on research projects.
 \item Published 5+ peer-reviewed papers in IEEE ICRA, RA-L, and related venues.
 \item Filed two patents on MRI-compatible robotic architectures.
\end{itemize}

\subsection{Researcher, University of Twente, Enschede}
{\small\textit{Robotics and Mechatronics, MURAB \& PanoSurg projects}} \hfill {\small Aug 2014--Nov 2015}
\begin{itemize}
 \item Designed and prototyped McRobot system for MRI-guided thorax interventions.
 \item Contributed to EU-funded MURAB project (MRI and Ultrasound Robotic Assisted Biopsy, EUR 4.34M project budget).
 \item Developed enhanced reality interfaces for minimally invasive procedures through PanoSurg, a EUR 50K Pioneers in Healthcare award.
 \item Implemented collision avoidance algorithms for human-robot collaboration.
\end{itemize}

\subsection{Researcher, TU Eindhoven}
{\small\textit{Control Systems Technology, Prof. Maarten Steinbuch}} \hfill {\small Aug 2012--Feb 2014}
\begin{itemize}
 \item System design of MRI-guided robots for minimally invasive surgery (McRobot project).
 \item Applied biomimicry principles to patient-mounted mechanisms for interventional procedures.
 \item Designed MRI-compatible force cells and sensors for surgical feedback.
 \item Supervised MSc students; contributed to grant proposals for medical robotics research.
\end{itemize}

\subsection{Research Assistant, Amirkabir University of Technology, Tehran}
{\small\textit{Biomedical Engineering Faculty, Motion Analysis Group}} \hfill {\small Jan 2006--Jan 2010}
\begin{itemize}
 \item Developed MRI-compatible robot designs for minimally invasive procedures.
 \item Created robots for radioactive agent injection and needle positioning.
 \item Contributed to exoskeleton robot design for rehabilitation.
\end{itemize}

\subsection{R\&D Project Director, Deble Co., Tehran}
\hfill {\small Jan 2004--Jun 2005}
\begin{itemize}
 \item Designed and prototyped a 3D printing system for construction using Iranian plaster (gatch).
 \item Managed system design, project planning, and experimental validation.
 \item Coordinated engineering team across mechanical, electrical, and control domains.
\end{itemize}

\section{Education}

\textbf{PhD} \hfill University of Twente, Enschede, 2016--2020 \\
{\small Surgical Robotics Laboratory, Faculty of Engineering Technology }

\vspace{4pt}
\textbf{MSc, Biomedical Engineering} \hfill Amirkabir University of Technology, Tehran, 2006--2009 \\
{\small Thesis: ``Design and prototyping of MRI/CT compatible robot for minimally invasive interventions'' \\
Supervisor: Prof. Rostami \quad Focus: Medical robotics in Motion Analysis Lab}

\vspace{4pt}
\textbf{BSc, Mechanical Engineering} \hfill Sharif University of Technology, Tehran, 2000--2006 \\
{\small Thesis: ``Design and prototyping of a construction assistance robot'' \quad Specialization: Solid State Design}

\section{Publications}

\begin{enumerate}[label={[\arabic*]}]
 \item ``Mechanism Design of a Patient-Mounted MRI-Compatible Robot''
 \item ``PneuAct-II: Hybrid Manufactured Electromagnetically Stealth Pneumatic Stepper Actuator''
 \item ``Dynamic Modeling of MRI-Compatible Assistant Surgery Robot''
 \item ``Introducing PneuAct: Parametrically-Designed MRI-Compatible Pneumatic Stepper Actuator''
 \item ``Primary Design of MRI-Compatible Needle for the purpose of soft tissue insertion''
 \item ``Frictional characteristics of Fusion Deposition Modeling (FDM) manufactured surfaces''
\end{enumerate}

\section{Patents}

\begin{enumerate}[label={[P\arabic*]}]
 \item MRI-compatible Surgery Assistant Robot
 \item Drugs Injection Smart Robot
\end{enumerate}

\section{Grants \& Funded Research}

\begin{itemize}
 \item \textbf{MURAB}, EU Horizon 2020, EUR 4.34M project budget (2015). MRI and Ultrasound Robotic Assisted Biopsy.
 \item \textbf{PneuARMM}, EUR 70K healthcare innovation grant, collaboration UT--MST Enschede (2018).
 \item \textbf{PanoSurg}, EUR 50K Pioneers in Healthcare award, collaboration UT--ZGT Hengelo (2015).
\end{itemize}

\section{Technical Skills}

\begin{tabularx}{\textwidth}{@{}lX@{}}
 \textbf{Programming:}  & Python (NumPy, SciPy, Jupyter), C\#/.NET/WPF/XAML, C/C++, MATLAB/Simulink/Octave, Fortran \\
 \textbf{CAD/CAE:}    & Siemens NX, SolidWorks, CATIA, FreeCAD, Inventor, Fusion 360, ANSYS, COMSOL, OpenFOAM, Elmer FEM \\
 \textbf{Simulation:}   & Modelica, Simulink, system modeling \\
 \textbf{Platforms:}   & Git, Linux, Windows, Docker \\
 \textbf{Documentation:} & \LaTeX, AsciiDoc, Markdown, LibreOffice, Inkscape, GIMP, Blender \\
 \textbf{Methodologies:} & Systems Engineering (V-model), Agile/Scrum, Lean Manufacturing, Concurrent Engineering \\
\end{tabularx}

\section{Open Source \& Community}

\begin{tabularx}{\textwidth}{@{}lX@{}}
 \textbf{GitHub:}     & 166 repositories, 490+ stars. Notable: Cmathtuts (438$\star$), NXOpen\_Python\_tutorials (75$\star$), awsomeEngSci (41$\star$), NXtips (37$\star$), Awesome-FLOSS-CAS (34$\star$), ModelicaPDE (20$\star$) \\
 \textbf{Stack Overflow:} & 14,467 reputation, 19 gold / 100 silver / 261 bronze badges. Top tags: Python, Windows, PyAudio, NumPy \\
 \textbf{FLOSS Advocacy:} & Maintainer of Awesome-FLOSS-CAS; open-source software advocate and contributor \\
\end{tabularx}

\section{Leadership \& Activities}

\begin{itemize}
 \item Chair of Surface Treatment Competence at NTS D\&E
 \item Research Funding Initiative Lead at NTS D\&E
 \item ASML Technology Angel Team member for strategic business roadmap
 \item Secretary of Iranian Network at University of Twente (IrNUT)
 \item Open source software advocate and contributor
\end{itemize}

\section{Languages}

English (professional working proficiency)\enspace$\cdot$\enspace
Dutch (elementary, A2)\enspace$\cdot$\enspace
Persian/Farsi (native)

\section{Industrial Internships}

\textbf{Saipa Press Co.}, Tehran \hfill Jul--Dec 2005 \\
{\small Robot maintenance for ABB robots with pneumatic end effectors.}

\vspace{4pt}
\textbf{ACECR-Sharif University Branch}, Tehran \hfill Jan--Jun 2002 \\
{\small Human-powered vehicles and ultra-light airplanes; mechanical design and power transmission.}

\section{References}

Available upon request.

\end{document}
