\documentclass[10pt,a4paper]{article}

\usepackage[margin=0.55in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{tabularx}

\definecolor{accent}{HTML}{2B5797}
\hypersetup{colorlinks=true,urlcolor=accent,linkcolor=accent}
\titleformat{\section}{\large\bfseries\color{accent}}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{6pt}{4pt}
\setlist[itemize]{nosep,left=0pt,label=\textbullet,topsep=2pt}
\pagestyle{empty}
\setlength{\parindent}{0pt}

\begin{document}

\begin{center}
  {\LARGE\bfseries Foad S. Farimani, PhD} \\[3pt]
  {\small Technical Program Manager\enspace$\mid$\enspace R\&D Leadership \& Systems Delivery\enspace$\mid$\enspace Dutch Citizen}
  \\[3pt]
  {\footnotesize
    Apeldoorn, Netherlands\enspace$\mid$\enspace
    +31\,614685010\enspace$\mid$\enspace
    \href{mailto:f.s.farimani@gmail.com}{f.s.farimani@gmail.com}\enspace$\mid$\enspace
    \href{https://linkedin.com/in/fsfarimani}{LinkedIn}\enspace$\mid$\enspace
    \href{https://github.com/Foadsf}{GitHub}\enspace$\mid$\enspace
    \href{https://stackoverflow.com/users/4999991}{Stack Overflow (14k+)}
  }
\end{center}

\section{Professional Summary}
Technical program manager with PhD-level research leadership and industrial project delivery in ASML's Tier-1 supply chain. Led cross-functional teams at NTS and VDL ETG, chaired competence groups, and drove research funding initiatives (Horizon Europe, NXTGEN). Secured \texteuro{}4.5M+ in grants across surgical robotics and semiconductor R\&D programs. Strong systems engineering background.

\section{Core Competencies}
\begin{center}
\small Program Management\enspace$\cdot$\enspace R\&D Strategy\enspace$\cdot$\enspace Stakeholder Management\enspace$\cdot$\enspace Horizon Europe / NXTGEN\enspace$\cdot$\enspace Risk Management\enspace$\cdot$\enspace Cross-Functional Teams\enspace$\cdot$\enspace Systems Engineering\enspace$\cdot$\enspace Budget Management\enspace$\cdot$\enspace Competence Leadership\enspace$\cdot$\enspace V-Model / Agile
\end{center}

\section{Professional Experience}

\textbf{System Lead Engineer} \hfill NTS D\&E (Norma), Hengelo \\
{\small\textit{Tier-1 ASML supplier}} \hfill {\small Mar 2022--Present}
\begin{itemize}
  \item Managed cross-functional engineering teams delivering advanced tooling for ASML DUV NXT and EUV NXE/EXE programs.
  \item Led Research Funding Initiative evaluating Horizon Europe and Nationaal Groeifonds NXTGEN opportunities.
  \item Chaired Surface Treatment Competence; member of ASML Technology Angel Team for strategic business roadmap.
  \item Drove continuous improvement initiatives and concurrent engineering processes.
\end{itemize}

\vspace{4pt}
\textbf{Lead Mechanical Engineer} \hfill VDL ETG T\&D, Hengelo \\
{\small\textit{ASML supplier --- precision opto-mechanical systems}} \hfill {\small Jul 2020--Feb 2022}
\begin{itemize}
  \item Designed opto-mechanical modules for ASML YieldStar 500 metrology system.
  \item Led engineering for EXE5000 cable slab module tooling and NXE3800 thermo-mechanical module.
\end{itemize}

\vspace{4pt}
\textbf{Doctoral Candidate \& Researcher} \hfill University of Twente, Enschede \\
{\small\textit{MRI-Compatible Surgical Robotics}} \hfill {\small Aug 2014--Mar 2020}
\begin{itemize}
  \item Managed multi-year research program with international collaborators across 4 institutions.
  \item Secured \texteuro{}120K+ in grants (PneuARMM \texteuro{}70K, PanoSurg \texteuro{}50K); contributed to \texteuro{}4.5M MURAB consortium.
  \item Supervised MSc/BSc students; coordinated clinical requirements with hospital partners (MST, ZGT).
\end{itemize}

\vspace{4pt}
\textbf{Researcher} \hfill TU Eindhoven \\
{\small\textit{MRI-guided minimally invasive surgical robots}} \hfill {\small Aug 2012--Feb 2014}
\begin{itemize}
  \item System design of MRI-guided robots; applied biomimicry to patient-mounted mechanisms.
\end{itemize}

\section{Education}

\textbf{MSc, Biomedical Engineering} --- Amirkabir University of Technology, Tehran \hfill 2006--2009 \\
{\small Thesis: Design and prototyping of MRI/CT compatible robot for minimally invasive interventions} \\[2pt]
\textbf{BSc, Mechanical Engineering} --- Sharif University of Technology, Tehran \hfill 2000--2006

\section{Key Achievements}

\begin{itemize}
  \item \textbf{Grants:} PneuARMM (\texteuro{}70K), PanoSurg (\texteuro{}50K), MURAB (EU Horizon 2020, \texteuro{}4.5M).
  \item \textbf{Patents:} MRI-compatible surgery assistant robot; Drug injection smart robot.
  \item \textbf{Delivery:} Led programs spanning ASML DUV NXT, EUV NXE/EXE, and YieldStar 500 platforms.
\end{itemize}

\section{Technical Skills}

{\small
\begin{tabularx}{\textwidth}{@{}lX@{}}
  \textbf{Languages:}  & Python, C\#/.NET, C/C++, MATLAB, Fortran \\
  \textbf{CAD/CAE:}     & Siemens NX, SolidWorks, CATIA, FreeCAD, ANSYS, OpenFOAM \\
  \textbf{Other:}       & \LaTeX, Git, Linux, Modelica, Simulink \\
  \textbf{Spoken:}      & English (professional), Dutch (A2), Persian (native) \\
\end{tabularx}
}

\end{document}
