\documentclass[11pt,a4paper]{article}

\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{tabularx}
\usepackage{fancyhdr}

\definecolor{accent}{HTML}{1A5276}
\hypersetup{colorlinks=true,urlcolor=accent,linkcolor=accent}
\titleformat{\section}{\Large\bfseries\color{accent}}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{10pt}{6pt}
\titleformat{\subsection}{\large\bfseries}{}{0em}{}
\titlespacing*{\subsection}{0pt}{6pt}{3pt}
\setlist[itemize]{nosep,left=0pt,label=\textbullet,topsep=2pt}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{\footnotesize Foad S. Farimani, Lead Mechanical Engineer CV, Page \thepage}
\setlength{\parindent}{0pt}

\begin{document}

\begin{center}
 {\LARGE\bfseries Foad S. Farimani, PhD} \\[4pt]
 {\small Lead Mechanical Engineer\enspace$\mid$\enspace Precision Mechanics, Tooling \& Semiconductor Equipment}
 \\[6pt]
 {\small
  Apeldoorn, Netherlands\enspace$\mid$\enspace
  Dutch citizen\enspace$\mid$\enspace
  +31\,614685010\enspace$\mid$\enspace
  \href{mailto:f.s.farimani@gmail.com}{f.s.farimani@gmail.com}\enspace$\mid$\enspace
  \href{https://linkedin.com/in/fsfarimani}{linkedin.com/in/fsfarimani}\enspace$\mid$\enspace
  \href{https://github.com/Foadsf}{github.com/Foadsf}
 }
\end{center}

\section{Professional Profile}
Lead Mechanical Engineer who turns ambiguous hardware problems into released, production-qualified designs for ASML lithography modules. At NTS D\&E and VDL ETG T\&D, delivered EXE5000 cable slab tooling, YieldStar 500 fiducial mechanics, NXE3800 heat shields, EXE:5000 E-pin fatigue resolution, qualification tooling, cooling plates, and sensor assembly coordination.

\section{Selected Mechanical Case Studies}

\begin{tabularx}{\textwidth}{@{}p{0.24\textwidth}X@{}}
\textbf{EXE5000 Cable-Slab Tooling} &
Led tooling workstreams across fixtures, hose and cable preforming, molds, CAD interfaces, supplier feedback, and manufacturability closure. The value was decomposing a dense, multi-interface tooling problem into practical engineering work packages. \\[4pt]
\textbf{YieldStar 500 Fiducials} &
Developed precision-mechanics concepts and calculation packages for fiducial interfaces, including leaf-spring stiffness, geometry trade-offs, and tolerance-sensitive optical/mechatronic interfaces. \\[4pt]
\textbf{NXE3800 Heat Shields} &
Supported NXE3800 heat-shield maturity through thermal, flow, bolt, defectivity, review, and release-documentation questions, including PDR/CDR/PIR/TPD/PMI context. \\[4pt]
\textbf{EXE:5000 E-pin Fatigue} &
Resolved a fatigue life risk in Inconel 718 folded leaf springs by tracing failures to EDM recast layer, coordinating plasma polishing and Kolsterising/K33 trials, and validating 2x life improvement on representative leaf springs; recognized at ASML's Technology Conference 2024. \\
\end{tabularx}

\section{Professional Experience}

\subsection{System Lead Engineer, NTS D\&E, Hengelo}
{\small\textit{Tier-1 ASML supplier, high-precision manufacturing systems}} \hfill {\small Mar 2022--Present}
\begin{itemize}
 \item Owned ASML module tooling workstreams covering M90 glue tooling, EXE:5000 cooling plates, qualification tooling, and EXE:5200 sensor assembly release coordination.
 \item Resolved a fatigue life risk in Inconel 718 E-pin folded leaf springs by tracing failures to EDM recast layer, coordinating plasma polishing and Kolsterising/K33 trials, and validating 2x life improvement on representative leaf springs; recognized at ASML's Technology Conference 2024.
 \item Chaired the Surface Treatment team and mapped supplier and process options for electropolishing, plasma polishing, passivation, acid etching, and precision cleaning.
 \item Standardized ASTM A380/A967 passivation route for YieldStar 500 Z-stage stainless-steel flexures and reduced surface-defect rework risk.
 \item Co-initiated engineering competence activity around FEM/CAE, fluidics/pneumatics, surface treatment, and mechanical-engineering knowledge sharing.
\end{itemize}

\subsection{Lead Mechanical Engineer, VDL ETG T\&D}
{\small\textit{Precision mechanics, tooling, and ASML equipment development}} \hfill {\small Jul 2020--Feb 2022}
\begin{itemize}
 \item Led mechanical engineering workstreams for EXE5000 cable slab integration tooling in a dense cable/hose assembly context.
 \item Developed precision-mechanics concepts and calculation packages for YieldStar 500 fiducial interfaces, including leaf-spring stiffness, geometry trade-offs, and tolerance-sensitive optical/mechatronic interfaces.
 \item Supported NXE3800 heat-shield maturity through thermal, flow, bolt, defectivity, review, and release-documentation questions.
 \item Contributed early-stage concept work around guiding systems, bellows behavior, pressure drop, and force-decoupler stiffness interpretation.
\end{itemize}

\subsection{PhD Researcher, University of Twente}
{\small\textit{MRI-compatible surgical robotics and pneumatic actuation}} \hfill {\small 2016--2020}
\begin{itemize}
 \item Designed MRI-compatible pneumatic actuators and patient-mounted robotic concepts using mechanical design, rapid prototyping, sensing, and experimental validation.
 \item Authored peer-reviewed work on MRI-compatible pneumatic actuation and developed patented MRI-compatible robotic concepts.
 \item Contributed to the EU Horizon 2020 MURAB consortium on MRI and ultrasound robotic assisted biopsy, with a EUR 4.34M project budget.
\end{itemize}

\subsection{Researcher, TU Eindhoven}
{\small\textit{MRI-guided minimally invasive surgical robotics}} \hfill {\small Aug 2012--Feb 2014}
\begin{itemize}
 \item Developed mechanical concepts for patient-mounted MRI-compatible robotic systems.
 \item Applied biomimicry, sensing, and mechanism-design principles to minimally invasive intervention concepts.
\end{itemize}

\section{Mechanical and Systems Skills}

\begin{tabularx}{\textwidth}{@{}lX@{}}
\textbf{Precision mechanics} & Leaf springs, compliant interfaces, fiducials, tooling, fixtures, molds, cleanroom handling, tolerance-sensitive assemblies \\
\textbf{Analysis} & Stiffness checks, bolt questions, thermal/flow reasoning, fatigue-root cause analysis, pressure-drop interpretation \\
\textbf{Semiconductor context} & ASML NXT/NXE/EXE, YieldStar 500, qualification tooling, PDR/CDR/PIR, TPD/PMI, 12NC/BOM awareness \\
\textbf{Tools} & Siemens NX, SolidWorks, CATIA, ANSYS/APDL context, MATLAB, Python, C\#/.NET, Git, \LaTeX \\
\end{tabularx}

\section{Education}
\textbf{PhD}, University of Twente, Enschede \hfill 2016--2020 \\
{\small Surgical Robotics Laboratory } \\[2pt]
\textbf{MSc, Biomedical Engineering}, Amirkabir University of Technology, Tehran \hfill 2006--2009 \\
\textbf{BSc, Mechanical Engineering}, Sharif University of Technology, Tehran \hfill 2000--2006

\section{Selected Publications and Patents}
\begin{itemize}
 \item Authored peer-reviewed publications on MRI-compatible pneumatic actuation, including PneuAct and PneuAct-II.
 \item Patent: MRI-Compatible Surgery Assistant Robot.
 \item Patent: Drugs Injection Smart Robot.
\end{itemize}

\end{document}
