\documentclass[10pt,a4paper]{article}

\usepackage[margin=0.55in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{tabularx}

\definecolor{accent}{HTML}{2B5797}
\hypersetup{colorlinks=true,urlcolor=accent,linkcolor=accent}
\titleformat{\section}{\large\bfseries\color{accent}}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{6pt}{4pt}
\setlist[itemize]{nosep,left=0pt,label=\textbullet,topsep=2pt}
\pagestyle{empty}
\setlength{\parindent}{0pt}

\begin{document}

\begin{center}
  {\LARGE\bfseries Foad S. Farimani, PhD} \\[3pt]
  {\small Lead Systems Engineer\enspace$\mid$\enspace Surgical Robotics \& Semiconductor Systems\enspace$\mid$\enspace Dutch Citizen}
  \\[3pt]
  {\footnotesize
    Apeldoorn, Netherlands\enspace$\mid$\enspace
    +31\,614685010\enspace$\mid$\enspace
    \href{mailto:f.s.farimani@gmail.com}{f.s.farimani@gmail.com}\enspace$\mid$\enspace
    \href{https://linkedin.com/in/fsfarimani}{LinkedIn}\enspace$\mid$\enspace
    \href{https://github.com/Foadsf}{GitHub}\enspace$\mid$\enspace
    \href{https://stackoverflow.com/users/4999991}{Stack Overflow (14k+)}
  }
\end{center}

\section{Professional Summary}
Systems engineer with 10+ years in medical robotics R\&D and high-precision semiconductor manufacturing. Led cross-functional teams at NTS developing tooling for ASML DUV/EUV systems. PhD research at University of Twente produced patented MRI-compatible surgical robots and secured \texteuro{}4.5M+ in EU/national grants. Chair of Surface Treatment Competence; experienced in Horizon Europe funding.

\section{Core Competencies}
\begin{center}
\small Systems Architecture\enspace$\cdot$\enspace Mechatronics\enspace$\cdot$\enspace Motion Control\enspace$\cdot$\enspace Air Bearings\enspace$\cdot$\enspace Precision Engineering\enspace$\cdot$\enspace MRI-Compatible Robotics\enspace$\cdot$\enspace Thermal Management\enspace$\cdot$\enspace Surface Treatment\enspace$\cdot$\enspace EU Grant Writing\enspace$\cdot$\enspace V\&V\enspace$\cdot$\enspace Siemens NX\enspace$\cdot$\enspace Python / C\#
\end{center}

\section{Professional Experience}

\textbf{System Lead Engineer} \hfill NTS D\&E (Norma), Hengelo \\
{\small\textit{Tier-1 ASML supplier}} \hfill {\small Mar 2022--Present}
\begin{itemize}
  \item Led cross-functional teams developing advanced tooling for ASML DUV NXT and EUV NXE/EXE lithography machines.
  \item Chair of Surface Treatment Competence, overseeing process optimization strategies.
  \item Led Research Funding Initiative, investigating Horizon Europe and NXTGEN incentives.
  \item Technical expertise in air bearings, mechatronics, motion control, fluidics, and thermal management.
\end{itemize}

\vspace{4pt}
\textbf{Lead Mechanical Engineer} \hfill VDL ETG T\&D, Hengelo \\
{\small\textit{ASML supplier --- precision opto-mechanical systems}} \hfill {\small Jul 2020--Feb 2022}
\begin{itemize}
  \item Designed opto-mechanical modules for ASML YieldStar 500 metrology system.
  \item Led engineering for EXE5000 cable slab module tooling and NXE3800 thermo-mechanical module.
\end{itemize}

\vspace{4pt}
\textbf{Doctoral Candidate \& Researcher} \hfill University of Twente, Enschede \\
{\small\textit{MRI-Compatible Surgical Robotics}} \hfill {\small Aug 2014--Mar 2020}
\begin{itemize}
  \item Developed PneuAct stepper actuators and PneuARMM robotic platform for MRI-guided surgery.
  \item Secured \texteuro{}70K healthcare innovation grant; contributed to MURAB project (\texteuro{}4.5M EU Horizon 2020).
  \item Published 5+ peer-reviewed papers (IEEE ICRA, RA-L); filed two patents.
\end{itemize}

\vspace{4pt}
\textbf{Researcher} \hfill TU Eindhoven \\
{\small\textit{MRI-guided minimally invasive surgical robots}} \hfill {\small Aug 2012--Feb 2014}
\begin{itemize}
  \item System design of MRI-guided robots; applied biomimicry to patient-mounted mechanisms.
\end{itemize}

\section{Education}

\textbf{MSc, Biomedical Engineering} --- Amirkabir University of Technology, Tehran \hfill 2006--2009 \\
{\small Thesis: Design and prototyping of MRI/CT compatible robot for minimally invasive interventions} \\[2pt]
\textbf{BSc, Mechanical Engineering} --- Sharif University of Technology, Tehran \hfill 2000--2006

\section{Key Achievements}

\begin{itemize}
  \item \textbf{Grants:} PneuARMM (\texteuro{}70K), PanoSurg (\texteuro{}50K), MURAB (EU Horizon 2020, \texteuro{}4.5M).
  \item \textbf{Patents:} MRI-compatible surgery assistant robot; Drug injection smart robot.
  \item \textbf{Leadership:} Chair of Surface Treatment Competence; ASML Technology Angel Team member.
\end{itemize}

\section{Technical Skills}

{\small
\begin{tabularx}{\textwidth}{@{}lX@{}}
  \textbf{Languages:}  & Python, C\#/.NET, C/C++, MATLAB, Fortran \\
  \textbf{CAD/CAE:}     & Siemens NX, SolidWorks, CATIA, FreeCAD, ANSYS, OpenFOAM \\
  \textbf{Other:}       & \LaTeX, Git, Linux, Modelica, Simulink \\
  \textbf{Spoken:}      & English (professional), Dutch (A2), Persian (native) \\
\end{tabularx}
}

\end{document}
